Staged Abstract Interpreter

### 2018-02-01 paper/paper.tex
add a related work
draft introduction section

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  It is well known that a staged interpreter is a compiler. A nature question is to ask that what would be for a staged abstract interpreter and how to do that.
\end{abstract}

@@

%% Keywords
%% comma separated list
\keywords{generic programming, abstract interpretation, static analysis}  %% \keywords are mandatory in final camera-ready submission

@@

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  It is well known that a staged interpreter is a compiler. A nature question is to ask 
  that what would be a staged abstract interpreter and how to obtain it in a mechanized 
  approach.

  In this paper, we systematically study the family of staged abstract interpreters, including 
  \citeauthor{Boucher:1996:ACN:647473.727587}'s Abstract Compilation, staged small-step 
  Abstracting Abstract Machines (AAM) and staged Abstracting Definitional Interpreters (ADI).
  To understand their relations, we firstly study the relations of their unstaged counterparts:
  we show how to obtain a abstracting definitional interpreter by a series of transformations
  from a small-step abstracting abstract machine. A key insight we show is how the pushdown 
  property of 
  analysis been obtained when transforming from small-step AAM to ADI, as well as how it 
  been lost in another direction.
  (TODO: pushdown for staged abstract interpreter?)

  We show staged abstract interpreters have practical applications rather than just theoretical merit.
  The time consumed of a analysis can be decreased by staging (TODO: to what degree). We evaluate
  the improvement of performance on benchmark programs.
  Another application of staged abstract interpreter is to transform whole-program analysis
  to modular analysis without losing precison. The generated code can be viewed as a 
  partially analyzed result, which also can be composed and used latter with other modulars
  in the program.

\end{abstract}

@@

%% Keywords
%% comma separated list
\keywords{staged computation, abstract interpretation, static analysis}  %% \keywords are mandatory in final camera-ready submission

@@

\citeauthor{hardekopf2011flow} apply staging to flow-sensitive pointer analysis \cite{hardekopf2011flow}. 
They firstly stage the program code to obtain a sparse representation, then conduct
the flow-sensitive analysis.
